module2graphsandPCA

### 2022-03-14 module2graphsandPCA.Rmd
did PCA on all scales

#PCA on all variables

@@

rotationsK
```

KPC_var <-data.frame(var_explainedK, row.names=names(rotationsK)) %>%
  tibble::rownames_to_column("Principal Component")

@@

 + 
  geom_line() + 
  xlab("Principal Component") + 
  ylab("Variance Explained") +
  ggtitle("Scree Plot") +
  ylim(0, 0.20)+
  xlim(0,5)

@@

>>>>

#PCA on Kahan scale

@@

rotationsK

@@

KPC_var <-data.frame(var_explainedK, row.names=names(rotationsK)) %>%
          tibble::rownames_to_column("PC")

KPC_var

qplot(c(1:12), var_explainedK) + 
  geom_line() + 
  xlab("Principal Component") + 
  ylab("Variance Explained") +
  ggtitle("Scree Plot") +
  ylim(0, 0.30)+
  xlim(1,7)

@@

```{r, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
# PCA test on qualities of the perceiver

ecopolscalepca <- ecopolscalescores %>%
  select(!starts_with(c("Risky","Gender","Caste","Religion","State")))%>%
  prcomp(center = TRUE,scale. = TRUE)

var_explained_ecopol = ecopolscalepca$sdev^2 / sum(ecopolscalepca$sdev^2)

summary(ecopolscalepca)

```
```{r, echo=FALSE}

rotationsecopol = ecopolscalepca["rotation"]
rotationsDFecopol <- do.call(rbind.data.frame, rotationsecopol)
rotationsDFecopol
```

qplot(c(1:11), var_explained_ecopol) + 
  geom_line() + 
  xlab("Principal Component") + 
  ylab("Variance Explained") +
  ggtitle("Scree Plot") +
  ylim(0.05, 0.20)+
  xlim(1,7)

```{r}

#PCA on Kahan scale

Solar <- codedmodule2 %>%
  select("DISPLACESOLAR":"RELYSOLAR")

#%>%
  separate(Var, c("prefix", "Var", "technology"), sep = c(0,-5), remove = T)%>%
  select(!"prefix")

ROOFS<- codedmodule2 %>%
  select("DISPLACEROOFS":"RELYROOFS")

# %>%
  pivot_longer(cols ="DISPLACEROOFS":"RELYROOFS", names_to = "Var", values_to = "score") %>%
  separate(Var, c("prefix", "Var", "technology"), sep = c(0,-5), remove = T)%>%
  select(!"prefix")

DIESEL<- codedmodule2 %>%
  select("DISPLACEDIESEL":"RELYDIESEL")%>%
  pivot_longer(cols ="DISPLACEDIESEL":"RELYDIESEL", names_to = "Var", values_to = "score") %>%
  separate(Var, c("prefix", "Var", "technology"), sep = c(0,-6), remove = T)%>%
  select(!"prefix")

FIREWOOD<- codedmodule2 %>%
  select("DISPLACEFIRE":"RELYFIRE")%>%
  pivot_longer(cols ="DISPLACEFIRE":"RELYFIRE", names_to = "Var", values_to = "score") %>%
  separate(Var, c("prefix", "Var", "technology"), sep = c(0,-8), remove = T)%>%
  select(!"prefix")

COAL<- codedmodule2 %>%
  select("DISPLACECOAL":"RELYCOAL")%>%
  pivot_longer(cols ="DISPLACECOAL":"RELYCOAL", names_to = "Var", values_to = "score") %>%
  separate(Var, c("prefix", "Var", "technology"), sep = c(0,-4), remove = T)%>%
  select(!"prefix")

NUCLEAR<- codedmodule2 %>%
  select("DISPLACENUCLEAR":"RELYNUCLEAR")%>%
  pivot_longer(cols ="DISPLACENUCLEAR":"RELYNUCLEAR", names_to = "Var", values_to = "score") %>%
  separate(Var, c("prefix", "Var", "technology"), sep = c(0,-7), remove = T)%>%
  select(!"prefix")

Solar.pca <- Solar %>%
  na.omit()%>%
  prcomp(center = TRUE, scale. = TRUE)

rotations = Solar.pca["rotation"]

#calculate total variance explained by each principal component
var_explainedSolar <- Solar.pca$sdev^2 / sum(Solar.pca$sdev^2)

rotationsSolar <- do.call(rbind.data.frame, rotations)

rotationsSolar

qplot(c(1:10), var_explainedSolar) + 
  geom_line() + 
  xlab("Principal Component") + 
  ylab("Variance Explained") +
  ggtitle("Scree Plot") +
  ylim(0.01, 0.40)+
  xlim(1,7)
